Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation

### 2023-12-28 mop/draft.tex
Updates from Overleaf

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.53]{imgs/095/pairs.png}
    \includegraphics[scale=0.53]{imgs/095/qq.png}
    \caption{Scatterplots depicting the performance of IFAD against that of IF2. Left: Paired searches from the same starting point. Right: Q-Q plot of ranked IFAD searches against ranked IF2 searches. It is clear that on average, IFAD has the edge, and manages to find the MLE while no IF2 search successfully gets within 5 log-likelihood units of it. }
    \label{fig:scatter}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics{imgs/095/boxplot.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics{imgs/095/optim.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

\begin{figure}[u]
    \centering
    \includegraphics{imgs/095/hist.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.53]{imgs/095/pairs.png}
    \includegraphics[scale=0.53]{imgs/095/qq.png}
    \caption{Scatterplots depicting the performance of IFAD against that of IF2. Left: Paired searches from the same starting point. Right: Q-Q plot of ranked IFAD searches against ranked IF2 searches. It is clear that on average, IFAD has the edge, and manages to find the MLE while no IF2 search successfully gets within 5 log-likelihood units of it. We use a dotted red line to display the MLE in both. }
    \label{fig:scatter}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.52]{imgs/095/boxplot.png}
    \includegraphics[scale=0.54]{imgs/095/optim.png}
    \caption{\textbf{Left:} Boxplot depicting the performance of IFAD and IF2 where we plot the results of the best run out of every ten runs. This simulates the result of the common procedure of running a few searches and choosing the best one. IFAD outperforms all other methods, and improves on the warm-start given by running 40 IF2 iterations. Our choice of hyperparameters for our implementation of IF2 outperforms the choices made by \cite{ionides15}, which we depict in the boxplot labeled "IF2 2015".
    \textbf{Right:} Optimization progress of IFAD and IF2, where the solid lines depict the median negative log-likelihood at each iteration and the shaded area depicts the 20\% and 80\% percentiles. The dashed orange line depicts the median warm-start given by running 40 IF2 iterations. While running 60 more iterations of IF2 improves upon the median warm-start, doing so ultimately underperforms
    In both, as before, we use a dotted red line to display the MLE. }
    \label{fig:boxplot-search}
\end{figure}

\begin{figure}[u]
    \centering
    \includegraphics[scale=0.7]{imgs/095/hist.png}
    \caption{Histogram comparison of the performance of IFAD, IF2, and MOP alone. As before, we note that IFAD Performing MOP alone }
    \label{fig:hist-all}
\end{figure}
